\thispagestyle{empty}
\newpage
\cleardoublepage\phantomsection
\addcontentsline{toc}{chapter}{Abstract}\index{Abstract}
\begin{center}
{\Large \bf Abstract}\\
\end{center}
\vspace{10pt}

\textbf{OpenArmor: Intelligent Cybersecurity Powered by Advanced Logging}

In today’s digital landscape, the rise of sophisticated cyber threats compels organizations to adopt stronger defenses. However, traditional security measures often struggle to keep up with the dynamic nature and complexity of modern attacks. To address these challenges, we introduce \textbf{OpenArmor}—an innovative cybersecurity solution that integrates advanced logging techniques with state-of-the-art artificial intelligence (AI) and machine learning (ML). This powerful combination enables proactive threat detection, automated analysis, and rapid response capabilities.

At its core, OpenArmor leverages the \textbf{extended Berkeley Packet Filter (eBPF)}, a cutting-edge kernel-level technology that allows efficient and comprehensive system activity logging. By extracting data directly from the Linux kernel, OpenArmor offers unparalleled visibility into system operations, capturing granular insights often overlooked by traditional logging methods. These detailed logs provide the foundation for OpenArmor’s advanced security analytics.

To ensure seamless integration with existing security infrastructures, OpenArmor structures its logs according to the \textbf{Open Cybersecurity Schema Framework (OCSF)}, a widely adopted industry standard. This compatibility allows OpenArmor to interface smoothly with security information and event management (SIEM) platforms, enabling organizations to maximize the value of their existing security tools while gaining enhanced threat detection capabilities.

The true strength of OpenArmor lies in its \textbf{AI- and ML-powered analytics}. Through advanced algorithms, the system establishes a dynamic baseline of normal system behavior, allowing it to detect even subtle anomalies that may indicate potential threats. This proactive detection ensures organizations stay ahead of attacks rather than reacting to them after the fact.

OpenArmor continuously monitors system activity, using AI to correlate events and recognize patterns indicative of security incidents. By automating these processes, it significantly reduces the burden on security teams, enabling them to focus on high-priority tasks while ensuring no potential threat goes undetected.

\newpage
Additionally, OpenArmor provides \textbf{intelligent alerts} with actionable insights, empowering security professionals to respond swiftly and effectively. These alerts are tailored to the specific needs of the organization, taking into account factors such as industry regulations, compliance requirements, and risk profiles. This ensures responses are efficient, targeted, and context-aware.

By combining advanced logging with AI and ML capabilities, OpenArmor offers a comprehensive, adaptive cybersecurity solution that continuously monitors, analyzes, and evolves with emerging threats. Its proactive threat detection, automated analysis, and contextual alerting system represent a paradigm shift in cybersecurity, reducing risk exposure and strengthening defenses.

OpenArmor marks the beginning of a new era in \textbf{intelligent cybersecurity}, enabling organizations to stay ahead of evolving threats. By leveraging the synergy between advanced logging and AI-powered analytics, OpenArmor provides a robust, adaptive security posture—protecting critical systems and data while allowing organizations to focus confidently on their core operations.
