% ACKNOWLEDGEMENT PAGE
\thispagestyle{empty}
\newpage
\cleardoublepage\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}\index{Acknowledgements}
\begin{center}
{\Large \bf Acknowledgements}\\
\end{center}
\vspace{10pt}

\begin{flushright}
\textit{"The single greatest cause of happiness is gratitude."}\\
\vspace{5mm}
— Auliq-Ice
\end{flushright}

The completion of this project would not have been possible without the help and support of many individuals and institutions. 

First, we sincerely thank our project guide, \textbf{Professor Ishan K. Rajani}, for his expert guidance, continuous encouragement, and unwavering support throughout the project. His patience, advice, and willingness to share knowledge were invaluable in shaping our work and overcoming various challenges. 

We also extend our heartfelt gratitude to the \textbf{CSE Department}, especially \textbf{Dr. Kruti Sutaria} and \textbf{Professor Yatin Shukla}, for their valuable feedback, insightful inputs, and assistance at various stages of the project. Their expertise significantly enriched our understanding.

Additionally, we are deeply grateful to the open-source community and the developers behind the technologies we utilized, such as \textbf{eBPF}, \textbf{OCSF}, and various AI/ML libraries. Their contributions were instrumental in facilitating our research and advancing cybersecurity innovation.

We would also like to thank our fellow students, whose time, efforts, and ideas greatly enhanced our group discussions and collaborations. Their diverse perspectives helped us refine and improve our work.

Finally, we owe profound gratitude to our families and friends for their unconditional love, encouragement, and motivation throughout this journey. Their belief in us provided the strength we needed to overcome challenges and persevere. 

This project would not have been possible without the collective efforts and contributions of all these individuals and institutions. We deeply appreciate their invaluable support.

\vspace{1.5cm}
\begin{flushright}
\textbf{Anubhav Gain (210303126225)}\\
\textbf{Hriday Sheth (210303124120)}\\
\textbf{Sharada Chiplunkar (210303126223)}\\
\textbf{Priyanshu Bhana (210303126222)}\\
CSE Department, PIET\\
Parul University,\\
Vadodara
\end{flushright}
