\chapter*{References}
\begin{enumerate}
\item Research Paper 1 
\\ \textbf{Title} : A Framework for eBPF-Based Network Functions in an Era of Microservices
\\ \textbf{Author} : Miano, S., Risso, F., Bernal, M. V., Bertrone, M., and Lu, Y. (2021). A framework for
eBPF-based network functions in an era of microservices. IEEE Transactions on Network and
Service Management, 18(1), 133-151.
\\ \textbf{Publishing Year} : 2021

\item Research Paper 2
\\ \textbf{Title} : A Framework for Document-level Cybersecurity Event Extraction \\ from Open Source Data
\\ \textbf{Author} :  Luo, N., Du, X., He, Y., Jiang, J., Wang, X., Jiang, Z., and Zhang, K. (2021, May). A
framework for document-level cybersecurity event extraction from open source data. In 2021 IEEE
24th International Conference on Computer Supported Cooperative Work in Design (CSCWD) (pp.
422-427). IEEE
\\ \textbf{Publishing Year} : May 2021

\item Research Paper 3
\\ \textbf{Title} : Distributed cloud monitoring using Docker as next generation container \\ virtualization
technology
\\ \textbf{Author} : Dhakate, S., and Godbole, A. (2015, December). Distributed cloud monitoring using
Docker as next generation container virtualization technology. In 2015 Annual IEEE India
Conference (INDICON) (pp. 1-5). IEEE
\\ \textbf{Publishing Year} : December 2015

\newpage
\item Research Paper 4 
\\ \textbf{Title} : AI-Driven Cybersecurity: An Overview, Security Intelligence Modeling and Research
Directions
\\ \textbf{Author} : Sarker, I. H., Furhad, M. H., and Nowrozy, R. (2021). Ai-driven cybersecurity: an
overview, security intelligence modeling and research directions. SN Computer Science, 2(3), 173.
\\ \textbf{Publishing Year} : 2021

\item Research Paper 5 
\\ \textbf{Title} : Unpacking strategic behavior in cyberspace: a schema-driven approach
\\ \textbf{Author} : Gomez, M. A., and Whyte, C. (2022). Unpacking strategic behavior in cyberspace: a
schema-driven approach. Journal of Cybersecurity, 8(1), tyac005.
\\ \textbf{Publishing Year} : 2022

\item Research Paper 6 
\\ \textbf{Title} : Developing a UI and Automation Framework for a Cybersecurity Research and
Experimentation Environment
\\ \textbf{Author} : Butler, C., Thompson, G., Hsieh, G., Hoppa, M. A., and Nauer, K. S. (2018). Developing
a UI and Automation Framework for a Cybersecurity Research and Experimentation Environment.
In Proceedings of the International Conference on Security and Management (SAM) (pp. 208-213).
The Steering Committee of The World Congress in Computer Science, Computer Engineering and
Applied Computing (WorldComp)
\\ \textbf{Publishing Year} : 2018

\item Research Paper 7 
\\ \textbf{Title} : Extracting rich semantic information about cybersecurity events
\\ \textbf{Author} : Satyapanich, T., Finin, T., and Ferraro, F. (2019, December). Extracting rich semantic
information about cybersecurity events. In 2019 IEEE International Conference on Big Data (Big
Data) (pp. 5034-5042). IEEE
\\ \textbf{Publishing Year} : December 2019

\newpage
\item Research Paper 8 
\\ \textbf{Title} : An autonomous cybersecurity framework for next-generation digital service chains
\\ \textbf{Author} : Repetto, M., Striccoli, D., Piro, G., Carrega, A., Boggia, G., and Bolla, R. (2021). An
autonomous cybersecurity framework for next-generation digital service chains. Journal of
Network and Systems Management, 29(4), 37
\\ \textbf{Publishing Year} : 2021

\item Research Paper 9 
\\ \textbf{Title} :  Integrating Cybersecurity Into a Big Data Ecosystem
\\ \textbf{Author} : Tall, A. M., Zou, C. C., and Wang, J. (2021, November). Integrating Cybersecurity Into a
Big Data Ecosystem. In MILCOM 2021-2021 IEEE Military Communications Conference
(MILCOM) (pp. 69-76). IEEE
\\ \textbf{Publishing Year} : November 2021

\item Research Paper 10 
\\ \textbf{Title} : Web of cybersecurity: Linking, locating, and discovering structured cybersecurity information
\\ \textbf{Author} : Takahashi, T., Panta, B., Kadobayashi, Y., and Nakao, K. (2018). Web of cybersecurity:
Linking, locating, and discovering structured cybersecurity information. International Journal of
Communication Systems, 31(3), e3470.
\\ \textbf{Publishing Year} : 2018

\newpage
\item eBPF: Extended Berkeley Packet Filter
\newline
	\href{https://ebpf.io/books/buzzing-across-space-illustrated-childrens-guide-to-ebpf.pdf}{eBPF Guide}

\item OCSF: Open Cyber Security Schema Framework
\newline
\href{https://schema.ocsf.io/  }{OSCF Schema}
\newline
\href{https://docs.aws.amazon.com/security-lake/latest/userguide/open-cybersecurity-schema-framework.html}{AWS Schema Framework for Reference}
\newline
\href{https://www.splunk.com/en_us/blog/security/open-cybersecurity-schema-framework-ocsf-takes-flight-with-v-1-schema-release.html}{Splunk Schema Framework Reference}

\item AI: Artificial Intelligence
\newline gpt-4
\newline
\href{https://huggingface.co/TheBloke/airoboros-13b-gpt4-1.4-SuperHOT-8K-GPTQ}{AI Tool}

\item GDPR: General Data Protection Regulation
\\
\href{https://www.consilium.europa.eu/en/policies/data-protection/data-protection-regulation/#:~:text=data%20protection%20rules-,What%20is%20the%20GDPR%3F,application%20on%2025%20May%202018.}{GDPR Policies}

\item HIPAA: Health Insurance Portability and Accountability Act
\\
\href{https://www.ncbi.nlm.nih.gov/books/NBK500019/}{HIPAA Policies}
\end{enumerate}
