% Table of Contents
\cleardoublepage
\phantomsection
\renewcommand{\contentsname}{Table of Contents}
\addcontentsline{toc}{chapter}{\contentsname}
\tableofcontents

% List of Abbreviations
% This section is now handled in the main.tex file

% List of Symbols
\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Symbols}
\chapter*{List of Symbols}
\begin{tabular}{@{}lp{0.8\textwidth}}
    $\alpha$ & Alpha (used for significance level in statistical tests) \\
    $\beta$ & Beta (used for type II error probability) \\
    $\gamma$ & Gamma (often used for the Euler-Mascheroni constant) \\
    $\delta$ & Delta (used to denote change or difference) \\
    $\epsilon$ & Epsilon (often used to denote a small positive quantity) \\
    $\zeta$ & Zeta (used in the Riemann zeta function) \\
    $\eta$ & Eta (often used for efficiency in physics) \\
    $\theta$ & Theta (often used for angles) \\
    $\lambda$ & Lambda (used in various contexts, including eigenvalues) \\
    $\mu$ & Mu (used for population mean) \\
    $\pi$ & Pi (ratio of a circle's circumference to its diameter) \\
    $\rho$ & Rho (often used for density or correlation coefficient) \\
    $\sigma$ & Sigma (used for standard deviation) \\
    $\tau$ & Tau (often used as an alternative to pi in some contexts) \\
    $\phi$ & Phi (often used for the golden ratio) \\
    $\chi$ & Chi (used in chi-squared distribution) \\
    $\psi$ & Psi (used in various contexts in physics and mathematics) \\
    $\omega$ & Omega (often used for angular velocity) \\
    $\exists$ & There exists
\end{tabular}

% List of Definitions
\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Definitions}
\chapter*{List of Definitions}
\begin{description}
    \item[Artificial Intelligence] The simulation of human intelligence processes by machines, especially computer systems.
    \item[Machine Learning] A subset of AI that provides systems the ability to automatically learn and improve from experience without being explicitly programmed.
    \item[Deep Learning] A subset of machine learning based on artificial neural networks with representation learning.
    \item[Cybersecurity] The practice of protecting systems, networks, and programs from digital attacks.
    \item[Big Data] Extremely large data sets that may be analyzed computationally to reveal patterns, trends, and associations.
    \item[Cloud Computing] The delivery of computing services over the Internet ("the cloud") to offer faster innovation, flexible resources, and economies of scale.
    \item[Blockchain] A decentralized, distributed ledger technology that records the provenance of a digital asset.
    \item[Quantum Computing] A type of computation that harnesses the collective properties of quantum states, such as superposition, interference, and entanglement, to perform calculations.
    \item[Edge Computing] A distributed computing paradigm that brings computation and data storage closer to the location where it is needed.
    \item[5G] The fifth generation technology standard for broadband cellular networks.
\end{description}

\cleardoublepage